Analysis paper

### 2021-06-03 analysis/analysis.Rmd
update plots

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline", 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
df[, (del_cols) := NULL]

@@

  p <- df[grepl(2, target)] %>%
    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
    geom_line() + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                            max(forecast_dates$full_hub_period)))

  return(p)
}

@@

```{r, eval = TRUE}
scores <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "target_type", "location_name", "horizon"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

scores %>%
  ggplot(aes(y = interval_score, x = horizon, color = model, 
             group = model)) + 
  geom_point() + 
  geom_line() + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_color_brewer(palette = "Accent") + 
  scale_y_log10() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")

>>>>

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline", 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))] %>%
  c("coverage_deviation")
df[, (del_cols) := NULL]

@@

  p <- df[grepl(2, target)] %>%
    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
    geom_line() + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                            max(forecast_dates$full_hub_period))) + 
    labs(y = "Median forecast", x = "Date")
  return(p)
}

@@

### Distribution of Bias over time

scores_target <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "target_type", "classification", "forecast_date")
)

p <- scores_target[model %in% regular_models] %>%
  distribution_plot_wis(x = "bias") + 
  scale_x_continuous() + 
  facet_wrap(~ target_phase, ncol = 3) + 
  geom_vline(xintercept = 0, color = "white", size = 1) + 
  labs(y = "Bias")

ggsave(here("analysis", "plots", "distribution_bias_phases.png"), plot = p)
```
